### 2025-01-20 acronyms/acronyms.tex
HEAD
HEAD error in file
acronyms
und acronyms

>>>>

\newacronym{ms}{MS}{Master of Science}
\newacronym{bs}{BS}{Bachelor of Science}
\newacronym{gsi}{GSI}{Graduate Student Instructor}
\newacronym{nrf}{NRF}{Naval Reactors Facility}
\newacronym{lnl}{LANL}{Los Alamos National Laboratory}
\newacronym{utk}{UTK}{University of Tennessee--Knoxville}
\newacronym{nna}{NNSA}{National Nuclear Security Administration}
\newacronym{byu}{BYU}{Brigham Young University}
\newacronym{usu}{USU}{Utah State University}
\newacronym{dod}{DOD}{Department of Defense}
\newacronym{pnl}{PNNL}{Pacific Northwest National Laboratory}
\newacronym{pr}{PR}{Proliferation Resistance}
\newacronym{pp}{PP}{Physical Protection}
\newacronym{dt}{DigitTwin}{Digital Twin}
\newacronym{ai}{AI}{Artificial Intelligence}
\newacronym{hitl}{HITL}{Human-in-the-Loop}
\newacronym{sra}{SRA}{Safety Risk Analysis}
\newacronym{rl}{RL}{Reinforcement Learning}
\newacronym{xai}{XAI}{Explainable Artificial Intelligence}
\newacronym{triga}{TRIGA}{Training, Research, Isotopes, General Atomics}
\newacronym{mars}{MARS}{Maintenance of Advanced Reactor Sensors and Components}
\newacronym{wsu}{WSU}{Washington State University}
\newacronym{irb}{IRB}{Institutional Review Board}
\newacronym{ddml}{DDML}{Data Driven Machine Learning}
\newacronym{und}{UND}{University of North Dakota}
\newacronym{dmp}{DMP}{Data Management Plan}
\newacronym{prm}{PRM}{Project Risk Management}
